---
title: "Data cleaning example"
author: "Your Name"
date: "June 61, 2016"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    code_folding: hide
params: 
  begin: "2013-02-15"
  end: "2013-03-15"
---
# Purpose

The purpose of this document is to illustrate cleaning a data set in a reproducible way using RMarkdown. 


```{r message = FALSE, warning = FALSE}
library(dplyr)
library(ggplot2)
library(lubridate)
library(nycflights13)
library(readr)
```

# Cleaning Process

For this analysis, we used only flights scheduled between ```r params$begin``` and ```r params$end```. 

```{r}
flights <- read_csv('flights.csv')
```

The initial table had ```r nrow(flights)``` records. The earliest one was scheduled for ```r min(flights$time_hour)```, and the latest for ```r max(flights$time_hour)```. 


Here is a quick visualization of your data selection as a portion of total volume over time. Is that what you expected? 

```{r}

flights <- flights %>% mutate(include = time_hour >= params$begin & time_hour < params$end) 
flights %>% ggplot() + 
	aes(x = month(time_hour, label = T), fill = include) + 
	geom_bar()

cleaned <- flights %>% filter(include)
```

The cleaned table now has ```r nrow(cleaned)``` records. The earliest one was scheduled for ```r min(cleaned$time_hour)```, and the latest for ```r max(cleaned$time_hour)```. 

```{r}

cleaned %>%
	write_csv('flights_CLEANED.csv')

```

