---
title: "Data cleaning example"
author: "Your Name"
date: "June 6, 2016"
output: html_document
---

# Purpose

The purpose of this document is to illustrate cleaning a data set in a reproducible way using RMarkdown. 

```{r libraries, messages = FALSE}
# Add ",warning = FALSE" to the chunk options to suppress the messages.  

library(dplyr)
library(lubridate)
library(nycflights13)
library(readr)
```

```{r params}

# This code block can be replaced by using report parameters instead. Add parameters to the YAML frontmatter like this: 

# params:
#   begin: "2013-02-01"

params <- list()
params$begin <- "2013-02-01" 
params$end <- "2013-03-01"

```

# Cleaning Process

We are basing our analysis on the `nycflights13` data set. The data look like this: 
```{r read_data}
# flights <- # FILL IN, the data is in flights.csv
glimpse(flights)
```

- The initial table had ```r nrow(flights)``` records. 
- The earliest one was scheduled for ```r min(flights$time_hour)```. 
- The latest one was scheduled for **FILL THIS IN, SEE BULLET ABOVE**. 

But for our analysis, we're only using flights scheduled between ```r params$begin``` and **FILL THIS IN TOO**. 

```{r clean_data}

cleaned <- flights %>% filter(time_hour >= params$begin,
							  time_hour < params$end)

```

The cleaned table has **FILL IN** records. The earliest one was scheduled for ```r min(cleaned$time_hour)```, and the latest for ```r max(cleaned$time_hour)```. 

```{r write_data}

cleaned %>% write_csv('flights_CLEANED.csv')
```

